Apparent preferences for cognitive effort fade when multiple forms of effort and delay are interleaved in a foraging environment

### 2020-08-06 Cost_manuscript.Rmd
quick note
added discussion notes from a couple of papers I found

**new** The adaptive nature of choices in this experiment demanded more flexibility than the single-parameter model fitted above. Based on the results, an adequate model of behavior should meet X criteria: 1) an initial preference for cognitive effort trials 2) that this preference disappeared as acceptances devolved to a common rate across costs; 3) show that participants kept track of recent offer history; 4) that these effects were robust to block order effects; 5) .... X) be applicable to both experiments

@@

- Talk about future experiments: if this is subjective time, changing the pacing of the tasks should change the acceptance rates for cognitive effort
- It's true that we didnt calibrate cog effort per subject. But instead we brought all subjects to the same level of performance, and we saw that as time progressed they became less likely to accept longer periods of effort.

>>>>

**new** The adaptive nature of choices in this experiment demanded more flexibility than the single-parameter model fitted above. Based on the results, an adequate model of behavior should meet X criteria: 1) an initial preference for cognitive effort trials 2) that this preference disappeared as acceptances devolved to a common rate across costs; 3) show that participants kept track of recent offer history; 4) that these effects were robust to block order effects; 5) deviations from optimality that were not simply due to overharvesting; and 6) be applicable to both experiments. Alternative foraging models from the literature were not fitted, as they did not qualitatively meet these criteria (wikenheiser, C&D, Fawcett...)

@@

- Working memory could produce timing issues (Buhi n Gershman). Efficiency couldn't be it because then global decrease wouldn't happen and phys effort might be affected too (Shenhav stuff). 
- Deviations in the willingness to pursue effort can predict depression relapse (https://jamanetwork.com/journals/jamapsychiatry/article-abstract/2761562), and motivational factors affecting effor aversion can be heterogenous between depression and schizophrenia (https://www.researchgate.net/publication/337361164_Pathways_to_Motivational_Impairments_in_Psychopathology_Common_Versus_Unique_Elements_Across_Domains). Like, the aversion is due to focusing on different elements of the task.
- Talk about future experiments: if this is subjective time, changing the pacing of the tasks should change the acceptance rates for cognitive effort
- It's true that we didnt calibrate cog effort per subject. But instead we brought all subjects to the same level of performance, and we saw that as time progressed they became less likely to accept longer periods of effort.
